### 2020-03-25 thesis_template/2_RelatedWork/relatedWork.tex
documentation on Rc dropping

>>>>

\begin{figure}[htb]
    \begin{lstlisting}
        struct OrderOwned {
            order_id: i32,
            num_items: i32, 
            payment: f64,
            order_time: f64,
            title: String,
            comment: String
        }

        struct OrderBorrowed<'a> {
            order_id: &'a i32,
            num_items: &'a i32, 
            payment: &'a f64,
            order_time: &'a f64,
            title: &'a String,
            comment: &'a String
        }

        struct OrderRc {
            order_id: Rc<i32>,
            num_items: Rc<i32>, 
            payment: Rc<f64>,
            order_time: Rc<f64>,
            title: Rc<String>,
            comment: Rc<String>
        }
    \end{lstlisting}
    \caption{Representation of Customer object in Rust.}
    \label{fig:Sampling}
\end{figure}

### 2020-03-25 thesis_template/3_Body/model/drop_ref_rc.tex
documentation on Rc dropping

\subsection{Evaluation}
In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.

The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.

In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value. 
Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.

Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.

\subsection{Result}
The result shows the time to drop borrowing reference is significatly faster than reference counting. This says that we should use borrwoing storategies whenever high performance computation is critical.
\begin{figure}[htb!]
    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
    \caption{Runtime for Droping to fields of Customer Object}
    \label{fig:Sampling}
\end{figure}

\subsection{Discussion}

>>>>

\subsection{Evaluation}
In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among reference and Rc. 
In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
Sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
The dropping of objects deletes references or Rcs which take role in fields the objects. However, it does not deallocate values to which they are pointing. 
Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.

\subsection{Result}
We generated 1M, 1.5M, 2M, 2.5M, 3M, 3.5M of CustomerBorrowed and CustomerRc objects and performed drop to them. 
The result in figure shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
This is because reference counters which are fields of CustomerRc have to check the number of reference pointing to the actual content and decide 
deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
The result shows the time to drop borrowing reference is significantly faster than reference counting. This says that we should use borrowing strategies whenever high performance computation is critical.
\begin{figure}[htb!]
    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
    \caption{Runtime for dropping Customer Object}
    \label{fig:Sampling}
\end{figure}

\subsection{Discussion}
In this experiment, an assessment is conducted to verify whether there is difference between behavior of borrowing and reference counting. 
These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
we can have reference with both strategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
However, the assumption here is that use of reference counting might be computationally expensive than borrowing, because reference counting has to track the number of reference pointing to the value. 
Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
